
% Lecture Template for ME3001-001-Tristan Hill - Spring 2017 - Fall 2017 - Fall 2020
% Mechanical Engineering Analysis with MATLAB
% Module 1 - Introduction 
% Topic 3 - Hello World

% Document settings

%\documentclass{beamer}                  % for presentation ?
\documentclass[handout]{beamer}  % for handout ?
\usepackage{/home/thill/Documents/lectures/analysis_lectures/analysis_lectures}

\newcommand{\MNUM}{1\hspace{2mm}} % Module number
\newcommand{\TNUM}{3\hspace{2mm}} % Topic number 
\newcommand{\moduletitle}{Introduction and MATLAB Review} % Titles and Stuff
\newcommand{\topictitle}{Hello World} 

\newcommand{\sectiontitleI}{What is a Program?} % More Titles and Stuff
\newcommand{\sectiontitleII}{Writing Your First Program}
\newcommand{\sectiontitleIII}{Step by Step Instructions}

\newcommand{\btVFill}{\vskip0pt plus 1filll}

% custom box
\newsavebox{\mybox}

\author{ME3001 - Mechanical Engineering Analysis} 
\title{Lecture Module - \moduletitle}
\date{Mechanical Engineering\vspc Tennessee Technological University}

\begin{document}
	
	\lstset{language=MATLAB,basicstyle=\ttfamily\small,showstringspaces=false}
	
	\frame{\titlepage \center\begin{framed}\Large \textbf{Topic \TNUM - \topictitle}\end{framed} \vspace{5mm}}
	
	% Section 0: Outline
	\frame{
		\large \textbf{Topic \TNUM - \topictitle} \vspace{3mm}\\
		
		\begin{itemize}
			
			\item \sectiontitleI    \vspc % Section I
			\item \sectiontitleII 	\vspc % Section II
			\item \sectiontitleIII 	\vspc %Section III
			%\item \sectiontitleIV 	\vspc %Section IV
			
		\end{itemize}
		
	}


\section{\sectiontitleI}

\frame{
  \frametitle{\sectiontitleI}
  	
		\begin{itemize}
			\item This word has several defintions. \\

			\item  In MATLAB we will refer to a program as a {\it script}	
		\end{itemize}

\newpage
	\vspace{10mm}
	\textbf{ You need to setup and manage a directory for this class!}
  	

}

\section{\sectiontitleII}

\frame{ \small
  \frametitle{\sectiontitleII}
  
 	\begin{enumerate}
			\item Open the {\bf MATLAB} application.
			
		
			\item In the {\it Editor} window. Click on the {\bf new } Button. Go down to {\bf script}.	
			
			\item Write a proper {\bf header} at the top of your script. Make sure to include your {\it Name}, the {\it Date}, the {\it Course}, and a {\it Description} of this program.
			
			\item In the {\it Editor} window. Click on the {\bf save} button. Now you will need to name your file and save it in your directory structure.
			
		
			\item Now you are going to start {\bf writing} your first program. 
			
			
			\item {\bf Run} your program and {\it watch the magic}!
		\end{enumerate}

}

\section{\sectiontitleIII}

\frame{ \small
  \frametitle{\sectiontitleIII}
  \textbf{Step 1} - Open the {\bf MATLAB} application.
  \vspace{40mm}
  }
  
  \frame{ \small
  \frametitle{\sectiontitleIII}
  \textbf{Step 2} - In the {\it Editor} window. Click on the {\bf new } Button. \vspace{3mm}\\ \hspace*{12mm}Go down to {\bf script}
  \vspace{40mm}
  }
  
  \frame{ \small
  \frametitle{\sectiontitleIII}
  \textbf{Step 3} - Write a proper {\bf header} at the top of your script. \vspace{3mm}\\ Make sure to include your {\it Name}, the {\it Date}, the {\it Course}, and a {\it Description} of this program.
  \vspace{40mm}
  }

   \frame{ \small
  \frametitle{\sectiontitleIII}
  \textbf{Step 4} - In the {\it Editor} window. Click on the {\bf save} button. \vspace{3mm}\\ Now you will need to name your file and save it in your directory structure.
  \vspace{40mm}
  }
   \frame{ \small
  \frametitle{\sectiontitleIII}
  \textbf{Step 5} - Now you are going to start {\bf writing} your first program. \vspace{3mm}\\ Make sure you are in the {\it Editor} window.
  \vspace{40mm}
  }
  \frame{ \small
  \frametitle{\sectiontitleIII}
  \textbf{Step 6} - {\bf Run} your program and {\it watch the magic}!
  \vspace{40mm}
  }
\end{document}

